\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-05-13 paper.qmd
Added author best model

>>>>

<!--Fit the best model for author suggestion and compute error-->
```{r}
## Compute hexbin parameters
num_bins_x_pbmc <- 30
lim1 <- pbmc_scaled_obj$lim1
lim2 <- pbmc_scaled_obj$lim2
r2_pbmc <- diff(lim2)/diff(lim1)

pbmc_model <- fit_highd_model(
  training_data = training_data_pbmc,
  emb_df = umap_pbmc_scaled,
  bin1 = num_bins_x_pbmc,
  q = 0.1,
  r2 = r2_pbmc,
  is_bin_centroid = TRUE,
  is_rm_lwd_hex = FALSE,
  col_start_highd = "PC_"
)

df_bin_centroids_pbmc <- pbmc_model$df_bin_centroids
df_bin_pbmc <- pbmc_model$df_bin

## Triangulate bin centroids
tr1_object_pbmc <- tri_bin_centroids(
  df_bin_centroids_pbmc, x = "c_x", y = "c_y")
tr_from_to_df_pbmc <- gen_edges(
  tri_object = tr1_object_pbmc)

## Compute 2D distances
distance_pbmc <- cal_2d_dist(
  tr_coord_df = tr_from_to_df_pbmc,
  start_x = "x_from",
  start_y = "y_from",
  end_x = "x_to",
  end_y = "y_to",
  select_vars = c("from", "to", "distance"))

## To find the benchmark value
benchmark_pbmc <- find_lg_benchmark(
  distance_edges = distance_pbmc,
  distance_col = "distance")

trimesh_removed_pbmc <- vis_rmlg_mesh(
  distance_edges = distance_pbmc,
  benchmark_value = benchmark_pbmc,
  tr_coord_df = tr_from_to_df_pbmc,
  distance_col = "distance") +
  #xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("a", sc_ltr_pos)

## Compute error
error_df <- augment(
  df_bin_centroids = df_bin_centroids_pbmc,
  df_bin = df_bin_pbmc,
  training_data = training_data_pbmc,
  newdata = NULL,
  type_NLDR = "PaCMAP",
  col_start = "PC_")

error_df <- error_df |>
  mutate(type = case_when(
    row_wise_abs_error <= 5 ~ "error 0-5",
    row_wise_abs_error <= 10 ~ "error 5-10",
    row_wise_abs_error <= 15 ~ "error 10-15",
    row_wise_abs_error <= 20 ~ "error 15-20",
    .default = "error greter than 20"
  )) |>
  mutate(type = factor(type, levels = c(
    "error 0-5", "error 5-10", "error 10-15", "error 15-20", "error greter than 20")))

## To join embedding
error_df <- error_df |>
  bind_cols(umap_pbmc_scaled |>
              select(-ID))

error_plot_pbmc <- error_df |>
  ggplot(aes(x = UMAP1,
             y = UMAP2,
             color = type,
             group = ID)) +
  geom_point(alpha=0.5,
             size = 0.1) +
  interior_annotation("b", sc_ltr_pos)

```

<!--bin1 = 30, bin2 = 29, b = 870, non_empty = 132-->
```{r}
#| echo: false
#| fig-cap: "(a) Model generated in the 2D space overlaid on UMAP data, and (b) high-D model error in model space."
#| label: fig-model-pbmc-author
#| fig-pos: H

trimesh_removed_pbmc + error_plot_pbmc + 
  plot_layout(guides='collect', ncol=2) &
  theme(legend.position='bottom')
```

### 2024-05-13 paper.tex
Fix the issue and mnist digit1 best model added
Added author best model

>>>>

\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/fig-umapauthor-1.pdf}

\caption{\label{fig-umapauthor}2D layout from UMAP applied for the
PBMC3k dataset. Is this a best representation of the original data?}

\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/fig-model-pbmc-author-1.pdf}

\caption{\label{fig-model-pbmc-author}(a) Model generated in the 2D
space overlaid on UMAP data, and (b) high-D model error in model space.}
